Reconstructing the Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-11-14 doc/paper-lcr.tex
more draft editing

External convergence is undetectable even
in strong lens systems:
the lensed image positions, shapes and relative fluxes are affected, but not
in an unambiguous way
\citep{FalcoEtal1985}.

In time delay lens systems, under the addition of an external convergence (and
appropriate re-scaling of the lens potential) the relative Fermat potential
between the images is {\it not} invariant. This means that the time delay
between the images changes, despite the invariance of the image positions and
fluxes. As such it is necessary to include $\kappa$ in the lens modelling, if
cosmological parameters are to be estimated accurately and precisely from
observed time delays \citep{SuyuEtal2010}. Mass distributions that are
physically associated with the lens galaxy will affect the stellar dynamics of
the lens galaxy, so that dynamical observations can break the internal
mass-sheet degeneracy by providing an additional estimate of the lens galaxy's
mass \citep[e.g.,][]{SuyuEtal2010}. In this work our aim is to quantify the
lensing effect of massive objects, regardless of their position along the line
of sight.

If there is external convergence present that is not included in the
lens modeling, then the time delay distance -- inferred assuming $\kappa
= 0$ -- will be $(1-\kappa)$ less than the true value of $\Dt$:
\be 
\label{eq:MassSheet:Dtbias}
\Dt^{\rm{true}}=(1-\kappa) \Dt^{{\kappax = 0}}.
\ee
We can hence estimate the true distance if we have  with additional
knowledge of $\kappa$. Since $\kappa$ is typically small the absolute
uncertainty on the estimate of $\kappa$ \correspends to the fractional
uncertainty with which time-delay distances can be \infered.

For type Ia supernovae, it is the magnification due to line of sight mass
structure that is a potential source of cosmographic error.
The relationship between convergence $\kappa$ and magnification $\mu$ is
\bea 
\mu &=&       \frac{1}{(1-\kappa)^2 - |\gamma|^2}, \notag \\
    &\approx& (1+2\kappa)
\label{eq:MassSheet:mag}
\eea
where we have used the facts that the magnitude of the gravitational
shear at any point is typically comparable to the magnitude of the 
convergence, and that both are typically small. 
Under these assumptions, the fractional uncertainty in the
inferred luminosity of a magnified source will be approximately  twice
the absolute uncertainty in the convergence~$\kappa$. These
relationships will allow us to put our results on convergence estimation
in context.

@@

\citet{HilbertEtal2009} calculated the lensing convergence using the
``lightcone'' dark matter only 
output of the \MS, providing 1.7 degree square 
mock sky maps of this
quantity. In this process, the dark matter density from the simulation
was projected onto a set of lens planes at discrete redshifts,
adaptively gridded and smoothed, and then the second derivatives of the 
lensing potential required for the components of the magnification
matrix were computed using a multiple lens plane ray tracing algorithm.
The first order approximation to this algorithm \citep[equation 17
of][]{HilbertEtal2009} gives the total convergence at a given sky
position~$\bmath{\theta}$ as the simple summation of the surface density
in each lens plane, weighted by the inverse critical surface density
$\Sigma_{\rm cr}$ for that plane's redshift:
\be
\kappa(\bmath{\theta}) = \sum_i \frac{\Sigma_i(\bmath{\theta})}
                                     {\Sigma_{\rm cr}(z_i,\zs)}.
\ee
This approximation was found to be accurate to a few percent or better
in $\kappa$, even on 30 arcsecond scales.

@@

We require a method for estimating the
convergence at any point on the sky, given a catalog of observed
galaxy properties such as positions, brightnesses, colours, and
possibly stellar masses and redshifts, for every galaxy in the field of
the lens, down to some magnitude limit. Since we cannot observe the
surface mass density of each halo directy, we need some way of
estimating the mass of each halo in the catalog, so that we can compute
its contribution to the total $\kappa$ along the line of sight \citep[as
in \eg][]{GunnarssonEtal2006,WongEtal2011,KarpenkaEtal2012}. 
This mass assignment recipe
will be uncertain, but can be calibrated with cosmological simulations, which
represent a significant additional source of information to what is present in
the data.

Transforming an observed photometometric galaxy catalogue into a 
catalogue of halo masses, positions, and redshifts, will enable us to
attempt a reconstruction of the convergence induced by every halo near a
line of sight. This is the subject of Section \ref{sec:model:halos}. We
also need to account for the mass in the Universe that is not associated
with the galaxies we can see -- this is the subject of Section
\ref{sec:model:voids}.

@@

Each halo in our catalogue then contributes to
the line of sight convergence by
\be
\label{eq:kappai}
\kappa_i =\Sigma_{i}/\Sigma_{\mathrm{cr}}(z_i,\zs),
\ee
where the critical surface density was defined in \Eref{eq:sigcrit}.
Following the first order approximation of \citet{HilbertEtal2009}
outlined in \Sref{sec:MS} above, we compute 
the total convergence from all the halos along the line
of sight using
\be 
\label{eq:kappasummu}
\kappah = \sum_{i} \kappa_i.
\ee

@@

We use the relation of \citet{BehrooziEtal2010} to infer halo masses
from stellar masses; the details of this \proceedure are outlined in 
\Aref{appendix:MSMH}. Given an uncertain stellar mass and redshift for
each galaxy in the  catalog, we draw a sample halo mass from the PDF
that describes this uncertainty  (\Eref{eq:mhalo-mstar})  and use
\Eref{eq:kappai} to compute its contribution to the convergence,
$\kappa_i$; this can be done for all the halos along the line of sight
and summed to give a sample value of $\kappah$;  repeatedly applying
this \proceedure allows us to build up a histogram of $\kappah$ values
consistent with the data, and hence characterize $\pr(\kappah|\data)$.

@@

While halos contribute a positive convergence to $\kappa$, voids contribute
a negative convergence. When a ray bundle passes through a  region of space
that is less dense than $\rho_{\rm mean}(z)$ the rays are de-focused\footnote{In
principle, the convergence caused by halos is also caused by the overdensity,
but we neglect this effect since halos are typically much more dense than the
intergalactic medium}. Whilst the  full ray-traced solution takes into account
the effect of voids, our reconstruction cannot -- the halo catalogue does not
include voids. In principle the absence of a halo could be taken to infer a
void, but the under-density of such a void is hard to infer. Neglecting voids
would lead to a heavily biased estimate of $\kappa$. Moreover, the halos in 
the model only add mass to the background density, and that background density
already accounts for all the mass in the Universe! In order to make voids
negative relative to the mean density, we must subtract a significant smooth
mass component. The problem is that we do not have a good model for the
density structure of that smooth component.

@@

\Fref{fig:jointkh-k} shows the joint distribution of $\kappah$ and $\kappa$
values for 100,000 randomly selected \MS lines of sight, assuming noise-free
halo masses and redshifts. In this case, the PDF $\pr(\kappah|\data)$ is a
delta function: to read off $\pr(\kappa|\data)$ we must take a thin horizontal
slice across this joint distribution. Note that the joint PDF plotted in this
figure is the product of  the conditional distribution that we need for
calibration, and also the prior PDF for $\kappah$ that we need to ensure that
the global distribution of $\kappah$ values is defaulted to in the case of
poor observational data. At fixed $\kappah$ we find in \Fref{fig:jointkh-k}
that the scatter in $\kapparay$ grows with $\kappah$; our reconstruction is
better at reproducing underdense lines of sight than overdense lines of sight.
The effect of ignoring voids and the smooth mass component is evident in this
plot: $\kappah$ is significantly higher than $\kappa$, at any given $\kappa$
value. Multiplying by $\pr(\kappah|\data)$ and integrating over $\kappah$
gives a PDF for $\kappa$ centred at the correct place, by construction.

@@

% Since voids are not included in the halo model approximation, $\kappah$
% is a biased estimator of $\kappa$, but this can be calibrated for using
% the \proceedure of \Sref{sec:model:voids}. Taking the reconstructed
% $\kappah$ for $10^{5}$ lines of sight we form the joint
% distribution, $\pr(\kappa,\kappah)$ and marginalize over $\pr(\kappah)$ to
% give $\pr(\kappa)$. 
%
% PJM: WTF? We just went through all of this in the previous section!
% We need to check that we are doing what we say we are.
%
% TEC: yes this doesn't need to be here again
%

@@

In an ensemble of $10^{4}$ reconstructed lines of sight, we find the the mean
bias to be $-9.5\times 10^{-6}$, and the mean width to be 0.0132. This is
approximately 1.8 times smaller than the width of the global $\pr(\kappa)$. 
We find that our inferred $\kappa$ PDFs are consistent with the global
$\kappa$ distribution; Figure \ref{fig:globaldist} shows that sampling from
$\pr(\kappa|\data)$ in 100,000 reconstructed lines of sight produces a
distribution of $\kappa$ values over the sky identical to the global
$\pr(\kappa)$. Given perfect knowledge of halo mass and redshift, the
calibration \proceedure provides an unbiased estimate of $\kappa$ that is
$\sim$2 times as precise as using the global $\pr(\kappa)$.

@@

\Fref{fig:where} shows the cumulative contribution to $\kappah$ as a function
of projected distance from the line of sight, magnitude and redshift. We find
that most of the convergence comes from halos whose galaxies are close to the
line of sight.  Over half of the  convergence typically comes from halos
within 30 arcseconds of the line of sight; by 2 arcminutes, this fraction is
85\%. The contribution from halos beyond 2 arcminutes is relatively constant
at a contribution of 0.008$\pm$0.003. We find that ignoring halos beyond 2
arcminutes has no effect on the precision of the reconstruction; this is shown
in \Fref{fig:radcut}. As a function of magnitude, we find that $\kappah$
is dominated by objects with magnitudes between $i=18$ and $i=24$. Objects
brighter than $i=18$ are either too rare, or too close to the observer, to
make a significant contribution to the convergence. Objects fainter than
$i=24$ are too small to be important, unless they are extremely close to the
line of sight, but we find that including halos fainter than $i=24$ does not
improve the reconstruction.  \Fref{fig:magcut} shows the scatter on
$\kappah-\kappa$ (where $\kappah$ is shifted so that its mean is zero) as a
function of reconstruction magnitude limit.

% Since these objects
% must be extremely close to the line of sight to make a non-zero $\kappah$
% contribution, it is likely that neglecting stellar mass and using a spherical
% NFW prescription are too naive to adequately reconstruct $\kappax$.
%
% PJM: the sentence above does not make sense!
%
We do
not expect a deeper survey to decrease the size of the uncertainty in mapping
$\kappah$ onto $\kappa$. Halos at all redshifts out to the source redshift
(1.4, here) contribute to the convergence, but the largest contribution comes from
halos with $z \sim z_{\rm source}/2$.

@@

While the \MS catalogs do already contain stellar masses for each galaxy, we
find that these are not well behaved at the low mass end due to unreasonably high dark matter stripping from satellite halos. We also wanted to be able to perform the functional test of
trying to recover the convergence having assumed the correct stellar
mass--halo mass relation. For these reasons, we assign a new stellar mass to
each halo in the \MS catalogs, according to the stellar mass--halo mass
relation of \citet{BehrooziEtal2010}. From this true  stellar mass we
simulate an observed stellar mass by drawing a sample from 
$\pr(\log{M^{*}_{\rm obs}}|\log{M^{*}_{\rm true}})$ which we take to be a
Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$. Where
a spectroscopic redshift exists stellar masses can be estimated with typical
uncertainties of 0.15 dex \citep{AugerEtal2009}; however with photometric
redshifts stellar mass uncertainties are typically three times as large. We
use $\sigma_{M_*}=0.15$ for halos with a spectroscopic redshift and
$\sigma_{M_*}=0.45$ otherwise. For photometric redshift errors we draw a
redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take to be a Gaussian
of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$
is the halo's true redshift in the \MS catalogue.

@@

The best possible reconstructions of $\kappa$ will come from having a
spectroscopic redshift for every single object in each field
(\Fref{fig:reconwidths}).  In terms of telescope time, such a reconstruction
would be prohibitively expensive, but we investigate this scenario as an ideal
case. Reconstructing the lines of sight with perfect knowledge of the redshift
but an uncertain stellar mass, we find that the width of $\pr(\kappa|\data)$
grows with the expectation value of $\kappa$ (\Fref{fig:widthsvsH}). The low
$\kappa$ lines of sight are relatively empty, and so there are few
opportunities for uncertainties in the halo masses to \propogate into $\kappa$
uncertainties. The median reconstruction width in this idealised situations is
0.0123; some 22\% of lines of sight would have a reconstruction width less
than 0.01.

@@

Inferring the stellar mass of a galaxy from its magnitude and colours requires
an estimate of how far away the galaxy is; without a spectroscopic redshift
the \infered stellar mass is less precise. However, obtaining photometry has
much lower observational cost; over the next few years several large area
photometric surveys will reach 24th magnitude \citep{Euclid,LSST}, these will
provide sufficient data to reconstruct lines of sight {\it without} additional
observations. In principle the photometric redshift is correlated with the
\infered stellar mass, however we do not model this effect since the
convergence from the outskirts of an individual halo is only weakly \dependant
on redshift at fixed mass: the redshift error has only a small effect on the
inferred $\pr(\kappa|\data)$ when compared to the effect of uncertain stellar
masses.  With only photometric redshifts the uncertainty on
$\kappah$ is much larger than in the spectrocopic case and this
\propogates into a broader $\pr(\kappa|\data)$, although the photometric
reconstruction still typically produces a 40\% improvement compared to the
precision of the global $\pr(\kappa)$ (\Fref{fig:widthsvsH}).

@@

While a fully photometric reconstruction provides useful constraints on
$\pr(\kappa|\data)$, targeted spectroscopy can provide addtional constraints
on the masses and redshifts of halos whose $\kappah$ contribution have the
largest absolute uncertainty. Obtaining spectra of bright ($i<22$) objects is
relatively fast with large telescopes: however, we find that if spectroscopic
redhsifts were known for all $i<22$ galaxies in our field the reconstruction
improves slightly upon the purely photometric reconstruction, although the
improvement can depend strongly on the details of the particular line of
sight. Obtaining spectra for fainter objects would be correspondingly more
expensive, but if spectroscopic redshifts could be obtained for all $i<23$
galaxies and all $i<24$ galaxies within 1 arcminute of the line of sight, the
$\pr(\kappa|\data)$ would be almost as good as having complete spectroscopic
coverage (\Fref{fig:reconwidths}). High $\kappa$ lines of sight benefit the
most from additional spectral coverage, since these LoS have the most
uncertain $\kappah$. Consistent with our previous findings the lowest $\kappa$
lines of sight have the most constrained $\kappa$ PDFs.

@@

While it is good to reconstruct $\kappa$ precisely, it is more important that
$\kappa$ is reconstructed accurately. 
We test the accuracy of our reconstructed $\pr(\kappa|\data)$ in the following
way: for each line of sight we shift the reconstructed $\pr(\kappa|\data)$ by
the line of sight's true value of $\kappa$ to give
$\pr(\kappa-\kappatrue|\data)$. Since the $\pr(\kappa-\kappatrue|\data)$ for
each line of sight is then an \independant estimator of zero, the PDFs can be
combined according to
\be
\label{eq:bias}
\mathcal{P}_N = \prod_{i=1}^N \pr_i(\kappa-\kappa_{\rm true})
\ee
In this section, we quantify the bias as the size of the deviation in the
expectation value of $\mathcal{P}_N$ from zero. If the bias of $\mathcal{P}_N$
is smaller than the half-width of $\mathcal{P}_N$, our $\kappa$ estimators can
be considered accurate. 
The point at which the modulus of the bias and the width of $\mathcal{P}_N$
are approximately equal gives an estimate of the number of objects which can
be combined before the measurement is limited by systematic error.

@@

We first consider a purely random selection of lines of sight. With the purely
photometric reconstruction, there is a small bias towards underestimating
$\kappa$: combining 6 targets the half-width and bias of $\mathcal{P}_{6}$
both equal 0.007. With targeted spectroscopic follow up this improves
slightly, for the combination of 8 sightlines the half-width and expectation
value  $\mathcal{P}_{8}$ equal 0.005.  If these lines of sight hosted time
delay lenses, the latter number would correspond to a systematic error of
0.5\% in time delay distance. Since the statistical distance uncertainties due
to lens modelling and time delay estimation are likely to be at the 3-4\%
level \citep{SuyuEtal2010},  only a sample containing 50 or more lenses would
be limited by the residual bias  following external convergence
reconstruction.

@@

We find that selecting the most tightly constrained lines of sight {\it
decreases} the bias -- our reconstruction is most \succesful for the lowest
$\kappa$ lines of sight. With photometry alone, the bias in this sample is
0.002. With targeted spectroscopic follow-up of the selected lines of sight
there is negligible improvement, since the best constrained lines of sight are
the most empty, and it is the high-$\kappa$ lines of sight that benefit the
most from spectroscopy. Photometry of the field is sufficient to adequately
select the best lines of sight for cosmology -- and doing so greatly increases
both the precision and accuracy of the cosmological constraints per system.
In the context of time delay distance accuracy given in the previous section,
the sample size would have to be 30 or so before this residual systematic
error was equal to the statistical uncertainty.

@@

By selecting only lines of sight with an external shear of $\gamma>0.03$ we
can test the impact of shear selection. We find that in this sample, $\kappa$
is systematically underestimated at the $\sim$0.01 level (corresponding to a
1\% systematic error in distance, significant in a sample of 12 lenses). 
Part of this effect is mitigated if only
the lines of sight with both $\gamma>0.03$ and sharp $\pr(\kappa|\data)$ are
used, but biases at the $\sim$0.005 level remain. Since our model does not
include shear constraints it is not surprising that selecting based on shear
can induce a bias. A more sophisticated model that includes the shear
recovered from the lens modelling may be less susceptible to this bias. The
cartoon selection model used here ($\gamma>0.03$) is likely to be a much
stronger selection than reality, but nevertheless it is worth noting that the
reconstruction \proceedure will be biased if lens selection functions are
extreme and unaccounted for.

@@

We have shown that reconstructing the matter due to halos along any line of
sight can improve the constraints on the external convergence along that line
of sight, with, depending on sample selection,  the width of
$\pr(\kappa|\data)$ being up to a factor of two smaller than the global
$\pr(\kappa)$, and  we have quantified the residual bias in the $\kappa$
estimates under our calibration assumptions. We now revisit these assumptions.

>>>>

\new{
In strong lens systems where the source is time variable, the images do not 
vary simultaneously; the optical path length for each image is different due
to relativistic and geometric effects. The difference in optical path length
causes a time-delay between the light curves of each image. \citeauthor{FalcoEtal1985}
showed that the presence of additional matter (in the form of a mass-sheet)
along the line of sight has no observable effect except to rescale the time-delays.
As such, it is necessary to include $\kappax$ in the lens modelling, if
cosmological parameters are to be estimated accurately and precisely from
observed time delays \citep{SuyuEtal2010}. 
}

If there is external convergence present that is not included in the
lens modeling, then the time delay distance -- inferred assuming $\kappax
= 0$ -- will be $(1-\kappax)$ more than the true value of $\Dt$:
\be 
\label{eq:MassSheet:Dtbias}
\Dt^{\rm{true}}=\frac{\Dt^{{\kappax = 0}}}{1-\kappax}.
\ee

We can hence estimate the true distance {\it only} if we have with additional
knowledge of $\kappax$. Since $\kappax$ is typically small the absolute
uncertainty on the estimate of $\kappax$ corresponds to the fractional
uncertainty with which time-delay distances can be \infered.

Mass distributions that are
physically associated with the lens galaxy will affect the stellar dynamics of
the lens galaxy, so that dynamical observations can break the internal
mass-sheet degeneracy by providing an additional estimate of the lens galaxy's
mass \citep[e.g.,][]{SuyuEtal2010}. In this work our aim is to quantify the
lensing effect of massive objects, regardless of their position along the line
of sight.

@@

\citet{HilbertEtal2009} calculated the lensing convergence using the
``lightcone'' dark matter only 
output of the \MS, providing 1.7 degree square 
mock sky maps of this
quantity. In this process, the dark matter density from the simulation
was projected onto a set of lens planes at discrete redshifts,
adaptively gridded and smoothed, and then the second derivatives of the 
lensing potential required for the components of the magnification
matrix were computed using a multiple lens plane ray tracing algorithm.
The first order approximation to this algorithm \citep[equation 17
of][]{HilbertEtal2009} gives the total convergence at a given sky
position~$\bmath{\theta}$ as the simple summation of the surface density
in each lens plane, weighted by the inverse critical surface density
$\Sigma_{\rm cr}$ for that plane's redshift:
\be
\kappax(\bmath{\theta}) = \sum_i \frac{\Sigma_i(\bmath{\theta})}
                                     {\Sigma_{\rm cr}(z_i,\zs)}.
\ee
This approximation was found to be accurate to a few percent or better
in $\kappax$, even on 30 arcsecond scales.

@@

We require a method for estimating the
convergence at any point on the sky, given a catalog of observed
galaxy properties such as positions, brightnesses, colours, and
possibly stellar masses and redshifts, for every galaxy in the field of
the lens, down to some magnitude limit. Since we cannot observe the
surface mass density of each halo directy, we need some way of
estimating the mass of each halo in the catalog, so that we can compute
its contribution to the total $\kappax$ along the line of sight \citep[as
in \eg][]{GunnarssonEtal2006,WongEtal2011,KarpenkaEtal2012}. 
This mass assignment recipe
will be uncertain, but can be calibrated with cosmological simulations, which
represent a significant additional source of information to what is present in
the data.

Transforming an observed photometometric galaxy catalogue into a 
catalogue of halo masses, positions, and redshifts, will enable us to
attempt a reconstruction of the convergence induced by every halo near a
line of sight. \new{We also need to account for the convergence due to dark structures and
the divergence due to voids; we do not model voids or dark structures, but their
effects are included statistically by calibration the the convergence in halos,
$\kappah$, against the ray-traced convergence, $\kappax$, for \MS lines of sight.}

@@

Each halo in our catalogue then contributes to
the line of sight convergence by
\be
\label{eq:kappai}
\kappa_i =\Sigma_{i}/\Sigma_{\mathrm{cr}}(z_i,\zs),
\ee
where the critical surface density was defined in \Eref{eq:sigcrit}.
Following the first order approximation of \citet{HilbertEtal2009}
outlined in \Sref{sec:MS} above, we compute 
the total convergence from all the halos along the line
of sight using
\be 
\label{eq:kappasummu}
\kappah = \sum_{i} \kappa_i.
\ee
\notes{Using the Born approximation, we approximate light rays as straight.}

@@

We use the relation of \citet{BehrooziEtal2010} to infer halo masses
from stellar masses; the details of this \proceedure are outlined in 
\Aref{appendix:MSMH}. Given an uncertain stellar mass and redshift for
each galaxy in the  catalog, we draw a sample halo mass from the PDF
that describes this uncertainty  (\Eref{eq:mhalo-mstar})  and use
\Eref{eq:kappai} to compute its contribution to the convergence,
$\kappa_i$; this can be done for all the halos along a specific line of sight
and summed to give a sample value of $\kappah$;  repeatedly applying
this \proceedure allows us to build up a histogram of $\kappah$ values
consistent with the data, and hence characterize $\pr(\kappah|\data)$.

@@

While halos contribute a positive convergence to $\kappa$, voids contribute
a negative convergence. When a ray bundle passes through a  region of space
that is less dense than $\rho_{\rm mean}(z)$ the rays are de-focused\footnote{In
principle, the convergence caused by halos is also caused by the overdensity,
but we neglect this effect since halos are typically much more dense than the
intergalactic medium}. Whilst the  full ray-traced solution takes into account
the effect of voids, our reconstruction cannot -- the halo catalogue does not
include voids. \new{In principle the absence of galaxies implies something about
the presence a void, but we do not attempt to use this information}. Neglecting voids
would lead to a heavily biased estimate of $\kappa$. Moreover, the halos in 
the model only add mass to the background density, and that background density
already accounts for all the mass in the Universe! In order to make voids
negative relative to the mean density, we must subtract a significant smooth
mass component. The problem is that we do not have a good model for the
density structure of that smooth component.

@@

\Fref{fig:jointkh-k} shows the joint distribution of $\kappah$ and $\kappa$
values for 100,000 randomly selected \MS lines of sight, assuming noise-free
halo masses and redshifts. In this case, the PDF $\pr(\kappah|\data)$ is a
delta function: to read off $\pr(\kappa|\data)$ we must take a thin horizontal
slice across this joint distribution. Note that the joint PDF plotted in this
figure is the product of  the conditional distribution that we need for
calibration, and also the prior PDF for $\kappah$ that we need to ensure that
the global distribution of $\kappah$ values is defaulted to in the case of
poor observational data. At fixed $\kappah$ we find in \Fref{fig:jointkh-k}
that the scatter in $\kappax$ grows with $\kappah$; our reconstruction is
better at reproducing underdense lines of sight than overdense lines of sight.
The effect of ignoring voids and the smooth mass component is evident in this
plot: $\kappah$ is significantly higher than $\kappa$, at any given $\kappa$
value. Multiplying by $\pr(\kappah|\data)$ and integrating over $\kappah$
gives a PDF for $\kappa$ centred at the correct place, by construction.

@@

@@

In an ensemble of $10^{5}$ reconstructed lines of sight, we find the the mean
bias to be $-9.5\times 10^{-6}$, and the mean width to be 0.01. This is
approximately 1.8 times smaller than the width of the global $\pr(\kappa)$. 
We find that our inferred $\kappa$ PDFs are consistent with the global
$\kappa$ distribution; Figure \ref{fig:globaldist} shows that sampling from
$\pr(\kappa|\data)$ in $10^{5}$ reconstructed lines of sight produces a
distribution of $\kappa$ values over the sky identical to the global
$\pr(\kappa)$. Given perfect knowledge of halo mass and redshift, the
calibration \proceedure provides an unbiased estimate of $\kappa$ that is
$\sim$2 times as precise as using the global $\pr(\kappa)$.

@@

\Fref{fig:where} shows the cumulative contribution to $\kappah$ as a function
of projected distance from the line of sight, magnitude and redshift. We find
that most of the convergence comes from halos whose galaxies are close to the
line of sight.  Over half of the  convergence typically comes from halos
within 30 arcseconds of the line of sight; by 2 arcminutes, this fraction is
85\%. The contribution from halos beyond 2 arcminutes is relatively constant
at a contribution of 0.008$\pm$0.003. We find that ignoring halos beyond 2
arcminutes has no effect on the precision of the reconstruction; this is shown
in \Fref{fig:radcut}. As a function of magnitude, we find that $\kappah$
is dominated by objects with magnitudes between $i=18$ and $i=24$. Objects
brighter than $i=18$ are either too rare, or too close to the observer, to
make a significant contribution to the convergence. Objects fainter than
$i=24$ are too small to be important, unless they are extremely close to the
line of sight, but we find that including halos fainter than $i=24$ does not
improve the reconstruction.  \Fref{fig:magcut} shows the scatter on
$\kappah-\kappa$ (where $\kappah$ is shifted so that its mean is zero) as a
function of reconstruction magnitude limit. We do
not expect a deeper survey to decrease the size of the uncertainty in mapping
$\kappah$ onto $\kappa$. Halos at all redshifts out to the source redshift
(1.4, here) contribute to the convergence, but the largest contribution comes from
halos with $z \sim z_{\rm source}/2$.

@@

While the \MS catalogs do already contain stellar masses for each galaxy, we
find that these are not well behaved at the low mass end due to unreasonably high dark matter stripping from satellite halos. We also wanted to be able to perform the functional test of
trying to recover the convergence having assumed the correct stellar
mass--halo mass relation. For these reasons, we assign a new stellar mass to
each halo in the \MS catalogs, according to the stellar mass--halo mass
relation of \citet{BehrooziEtal2010}. From this true  stellar mass we
simulate an observed stellar mass by drawing a sample from 
$\pr(\log{M^{*}_{\rm obs}}|\log{M^{*}_{\rm true}})$ which we take to be a
Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$. Where
a spectroscopic redshift exists stellar masses can be estimated with typical
uncertainties of 0.15 dex \citep{AugerEtal2009}; however with photometric
redshifts stellar mass uncertainties are typically three times as large. We
use $\sigma_{M_*}=0.15$ dex for halos with a spectroscopic redshift and
$\sigma_{M_*}=0.45$ dex otherwise. For photometric redshift errors we draw a
redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take to be a Gaussian
of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$
is the halo's true redshift in the \MS catalogue.

@@

The best possible reconstructions of $\kappa$ will come from having a
spectroscopic redshift for every single object in each field
(\Fref{fig:reconwidths}).  In terms of telescope time, such a reconstruction
would be prohibitively expensive, but we investigate this scenario as an ideal
case. Reconstructing the lines of sight with perfect knowledge of the redshift
but an uncertain stellar mass, we find that the width of $\pr(\kappa|\data)$
grows with the expectation value of $\kappa$ (\Fref{fig:widthsvsH}). The low
$\kappa$ lines of sight are relatively empty, and so there are few
opportunities for uncertainties in the halo masses to \propogate into $\kappa$
uncertainties. The median reconstruction width in this idealised situations is
0.01; some 22\% of lines of sight would have a reconstruction width less
than 0.01.

@@

Inferring the stellar mass of a galaxy from its magnitude and colours requires
an estimate of how far away the galaxy is; without a spectroscopic redshift
the \infered stellar mass is less precise. However, obtaining photometry has
much lower observational cost; over the next few years several large area
photometric surveys will reach 24th magnitude \citep{Euclid,LSST}, these will
provide sufficient data to reconstruct lines of sight {\it without} additional
observations. In principle the photometric redshift is correlated with the
\infered stellar mass, however we do not model this effect since the
convergence from the outskirts of an individual halo is only weakly \dependant
on redshift at fixed mass: the redshift error has only a small effect on the
inferred $\pr(\kappa|\data)$ when compared to the effect of uncertain stellar
masses.  With only photometric redshifts the uncertainty on
$\kappah$ is larger than in the spectrocopic case and this
\propogates into a broader $\pr(\kappa|\data)$, although the photometric
reconstruction still typically produces a 50\% improvement compared to the
precision of the global $\pr(\kappa)$ (\Fref{fig:widthsvsH}).

@@

While a fully photometric reconstruction provides useful constraints on
$\pr(\kappa|\data)$, targeted spectroscopy can provide addtional constraints
on the masses and redshifts of halos whose $\kappah$ contribution have the
largest absolute uncertainty. Obtaining spectra of bright ($i<22$) objects is
relatively fast with large telescopes: however, we find that if spectroscopic
redshifts were known for all $i<22$ galaxies in our field the reconstruction
improves slightly upon the purely photometric reconstruction, although the
improvement can depend strongly on the details of the particular line of
sight. Obtaining spectra for fainter objects would be correspondingly more
expensive, but if spectroscopic redshifts could be obtained for all $i<23$
galaxies and all $i<24$ galaxies within 1 arcminute of the line of sight, the
$\pr(\kappa|\data)$ would be almost as good as having complete spectroscopic
coverage (\Fref{fig:reconwidths}). High $\kappa$ lines of sight benefit the
most from additional spectral coverage, since these LoS have the most
uncertain $\kappah$. Consistent with our previous findings the lowest $\kappa$
lines of sight have the most constrained $\kappa$ PDFs.

@@

While it is good to reconstruct $\kappa$ precisely, it is more important that
$\kappa$ is reconstructed accurately. The reconstruction must not be biased. 
We test the accuracy of our reconstructed $\pr(\kappa|\data)$ in the following
way: for each line of sight we have an estimator for the true convergence along
that line of sight, by subtracting the line of sight's ray-traced convergence
$\kappatrue$ from $\pr(\kappa|\data)$ we have an estimator of zero, $\pr(\kappa-\kappatrue|\data)$.
 Since the $\pr(\kappa-\kappatrue|\data)$ for
each line of sight is an \independant estimator of zero, the PDFs from $N$ lines of sight
can be combined according to
\be
\label{eq:bias}
\mathcal{P}_N = \prod_{i=1}^N \pr_i(\kappa-\kappa_{\rm true})
\ee
In this section, we quantify the bias as the size of the deviation in the
expectation value of $\mathcal{P}_N$ from zero. If the bias of $\mathcal{P}_N$
is smaller than the half-width of $\mathcal{P}_N$, our $\kappa$ estimators can
be considered accurate. Since the width of $\mathcal{P}_N$ decreases as more
lenses are combined a small bias will eventually be found for all estimators
In the context of measuring time delay distance at the one percent level the
expectation value of $|\mathcal{P}_N|$ needs to be less than 0.01.

@@

We first consider a purely random selection of lines of sight. With the purely
photometric reconstruction, there is no evidence of bias, even after combining 20
lines of sight. If these lines of sight hosted time
delay lenses, the bias number would correspond to a systematic error of
0.5\% in time delay distance. Since the statistical distance uncertainties due
to lens modelling and time delay estimation are likely to be at the 3-4\%
level \citep{SuyuEtal2010},  only a sample containing 200 or more lenses would
be limited by the residual bias  following external convergence
reconstruction.

@@

We find that selecting the most tightly constrained lines of sight has no impact on the
bias -- our reconstruction is most \succesful for the lowest
$\kappa$ lines of sight. With targeted spectroscopic follow-up of the selected lines of sight
there is negligible improvement compared to photometry alone, since the best constrained lines of sight are
the most empty, and it is the high-$\kappa$ lines of sight that benefit the
most from spectroscopy. Photometry of the field is sufficient to adequately
select the best lines of sight for cosmology -- and doing so greatly increases
 the precision of the cosmological constraints per system, with no degredation of the accuracy.
Since lenses are typically found in locally overdense environments, it is unlikely that 
an almost empty line of sight would contain a lens; it is somewhat optimistic to 
suggest that nearly empty lines of sight could be used for time-delay cosmology.

@@

By selecting only lines of sight with an external shear of $\gammax>0.03$ we
can test the impact of shear selection. We find that in this sample, $\kappax$
is systematically underestimated at the $\sim$0.003 level (corresponding to a
0.3\% systematic error in distance; in the absence of other sources of uncertainty, this
systematic error would be significant in a sample of 40 lenses). 
This effect is mitigated if only
the lines of sight with both $\gammax>0.03$ and well constrained $\pr(\kappax|\data)$ are
used, but biases at the $\sim$0.001 level remain. Since our model does not
include shear constraints it is not surprising that a selection function based on shear
can induce a bias. A more sophisticated model that includes the shear
recovered from the lens modelling may be less susceptible to this bias. The
toy selection model used here ($\gammax>0.03$) is likely to be a much
stronger selection than reality, but nevertheless it is worth noting that the
reconstruction \proceedure will be biased if lens selection functions are
extreme and unaccounted for.

@@

We have shown that reconstructing the matter due to halos along any line of
sight can improve the constraints on the external convergence along that line
of sight, with, depending on sample selection,  the width of
$\pr(\kappax|\data)$ being up to a factor of two smaller than the global
$\pr(\kappax)$, and  we have quantified the residual bias in the $\kappax$
estimates under our calibration assumptions. We now revisit these assumptions.
